MFCCs, Chroma Features, and Spectrogram Images for Deepfake Audio Classification Using Machine Learning

### 2024-12-05 paper/paper.tex
change in referencing waveforms
added deep explanation of spectrograms

\subsection{Mel-Spectrogram Images}
A Mel-Spectrogram image is an alternative method for visually representing sound. Generally, we see sound visualized as a two-dimensional waveform showing amplitude over time. Similar to MFCCs, Mel-Spectrograms are generated by performing a number of transformations on an audio sample, then representing the results as a graph.

>>>>

\subsection{Mel-Spectrogram Images}
A Mel-Spectrogram image is an alternative method for visually representing sound. Generally, we see sound visualized as a two-dimensional waveform showing amplitude over time. Figure~\ref{fig:real_waveform} shows an example of a "real" audio sample as a commonly seen waveform. Conversely, figure~\ref{fig:fake_waveform} shows an example of a "fake" audio sample as a waveform. While these representations are helpful, they do not provide enough information for a model to be able to make a decision.

A spectrogram is a representation of an audio signal as its frequency spectrum varies over time. Similar to MFCCs, Mel-Spectrograms are generated by performing a number of transformations on an audio sample, then representing the results as a graph. First, the audio is divided into short segments of time. We used approximately 93 ms segments. Then, a Hamming window is applied to each segment.

The Hamming window can be found with the following formula \cite{9252126}:
\begin{equation}
w(n) = \alpha_0 - (1 - \alpha_0) \cos\left(\frac{2\pi n}{N-1}\right), \quad 0 \leq n \leq N-1
\end{equation}
where \(\alpha_0 = \frac{25}{46}\), and \(N\) is the window length.

Following this operation, Fast Fourier transform (FFT) is applied to calculate the power spectrum of each frame. Lastly, we can obtain the Mel-Spectrogram by applying the Mel filter bank. Frequencies are convered to the Mel scale using the following formula \cite{9252126}:
\begin{equation}
\text{mel} = 2595 \, \lg\left(1 + \frac{f}{700}\right)
\end{equation}
